### 2018-05-21 Paper/examples.tex
..

To verify the accuracy of the third-order PCE, we estimate the relative L-2
norm of the difference between predictions of  $g(\bm{X})$, obtained using the
actual function in ~\eqref{eq:limit} and the 
PCE using~\eqref{eq:l2}~\alennote{Do we use a validation set?}  The
value of $\epsilon_{\mbox{\tiny{L-2}}}$ using evaluations 
at 100 points~\alennote{How are these points generated? Monte Carlo? QMC?}
was
found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
Furthermore, the accuracy is assessed in a probabilistic sense by comparing
PDFs of $g(\bm{X})$, obtained using the function and the 3D PCE as illustrated
in Figure~\ref{fig:conv_osc}~(right).  Clearly, the two PDFs are in excellent
agreement with each other. Hence, the ROS constructed using the methodology
presented in section~\ref{sec:method} could be used reliably to 
quantify the uncertainty in $g(\bm{X})$.
% due to parametric uncertainty
%associated with its functional description in~\eqref{eq:limit}, efficiently.

>>>>

To verify the accuracy of the third-order PCE, we estimate the relative L-2
norm of the difference between predictions of  $g(\bm{X})$, obtained using the
actual function in \eqref{eq:limit} and the 
PCE using \eqref{eq:l2}, and a validation test suite. The test suite comprised
model evaluations at 100 independent Monte-Carlo samples in the full 
parameter space. The value of $\epsilon_{\mbox{\tiny{L-2}}}$ 
was found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
Furthermore, the accuracy is assessed in a probabilistic sense by comparing
PDFs of $g(\bm{X})$, obtained using the function and the 3D PCE as illustrated
in Figure~\ref{fig:conv_osc}~(right).  Clearly, the two PDFs are in excellent
agreement with each other. Hence, the ROS constructed using the methodology
presented in section~\ref{sec:method} could be used reliably to 
quantify the uncertainty in $g(\bm{X})$.
% due to parametric uncertainty
%associated with its functional description in~\eqref{eq:limit}, efficiently.
